\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-11 paper/main.tex
.

As we want to learn from the similarity of drug side effects and
protein phenotypes, we use a deep half-twin neural network with a
contrastive loss using cosine similarity.  A half-twin neural network
aims to learn a similarity between two embeddings of the same
dimension.  The precomputed embeddings may have different
dimensionality and we first process them using a fully connected neural network
layer which takes as input an embedding and outputs a representation
of a particular size.
We use this as a trainable feature transformation.

An example structure for both types of features
can be found in Figure~\ref{fig:HalfTwinNetwork}. We use this LFT to
reduce the representation size of the embeddings for drugs and
proteins separately.
% While a regular deep neural network, denoted by LFT, for feature space reduction is not particularly novel, we
The use of an LFT enables flexible experimentation as both ontology
and molecular feature for both drugs and proteins are reduced to
the same dimensionality for varying sizes of inputs; this allows for a
high amount of modularity across different experimental setups by
adding different kinds of features into the model. Additionally, the
generated features may be used for other tasks. % ; for
% example, the ontology LFT can be reused for a variety of DL2vec-based
% features with respect to other ontologies and hypotheses
We follow the results of \textit{DL2vec} \cite{} and use as
activation function $\sigma := \mathrm{LeakyReLU}$ which leads to
improved performance compared to other activation functions.

>>>>

As we want to learn from the similarity of drug side effects and
protein phenotypes, we use a deep half-twin neural network with a
contrastive loss using cosine similarity.  A half-twin neural network
aims to learn a similarity between two embeddings of the same
dimension.  The precomputed embeddings may have different
dimensionality and we first process them using a fully connected
neural network layer which takes as input an embedding and outputs a
representation of a particular size, i.e., we use this layer as a
trainable feature transformation and apply it to reduce the
representation size of the embeddings for drugs and proteins
separately.  An example structure for both types of features can be
found in Figure~\ref{fig:HalfTwinNetwork}.
% While a regular deep neural network, denoted by LFT, for feature space reduction is not particularly novel, we
The use of this trainable feature transformation layer enables
flexible experimentation as both ontology and molecular feature for
both drugs and proteins are reduced to the same dimensionality for
varying sizes of inputs; this allows for a high amount of modularity
across different experimental setups by adding different kinds of
features into the model. Additionally, the generated features may be
used for other tasks. % ; for
% example, the ontology LFT can be reused for a variety of DL2vec-based
% features with respect to other ontologies and hypotheses
We follow the results of \textit{DL2vec} \cite{} and use as
activation function $\sigma := \mathrm{LeakyReLU}$ which leads to
improved performance compared to other activation functions.
